### 2025-09-07 submissions/03-jpam-RR/manuscript_main.tex
addressed R1's comments

I measure Asian racial identity using Current Population Survey (CPS) data from 2004-2021, enabling construction of objective Asian ancestry measures for minors living with parents. Following \textcite{antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020}, I utilize birthplace information for individuals, parents, and grandparents to create objective Asian ancestry indicators.\footnote{This approach parallels previous research but focuses on racial rather than ethnic categorization.} The methodology allows perfect identification of first-, second-, and third-generation Asian Americans (see Figure \ref{fig:diag} for visual representation). This approach enables construction of objective Asian ancestry measures for minors under age 17 living with parents.

The objective ancestry measure—distinct from subjective racial identification where respondents select ``Asian'' as their race—depends on birthplaces across three generations. The three identifiable generations include: 1) first-generation immigrants born in Asian countries with both parents also born in Asian countries, 2) second-generation individuals who are US-born citizens with at least one parent born in an Asian country, 3) third-generation Asian Americans who are US-born citizens with two US-born parents and at least one grandparent born in an Asian country. It is important to note that while the ancestry measure provides an objective assessment of Asian heritage, it may not capture all nuances of racial identity. For instance, White individuals with Asian ancestry born to non-Asian parents in Asia, such as on American military bases, may not be classified as Asian in the data. To avoid potential misclassification, I remove individuals who report that they were born abroad of American parents. The sample includes Asian Americans, first-, second-, and third-generation immigrants aged 17 and younger living with parents between 2004 and 2021. Summary statistics appear in Table (\ref{tab:sumstat1}).

While CPS relies on household respondents (parents or caregivers) to report children's racial identity, this proxy reporting likely reflects children's actual identity since parents significantly influence identity formation. \textcite{duncanIntermarriageIntergenerationalTransmission2011} support this perspective, demonstrating no variation in Asian identification based on household respondent type. The data confirms consistent Asian identity reporting regardless of whether mother (72\%), father (72\%), or child/other caregiver (87\%) serves as respondent, as shown in Table \ref{tab:hispbyproxy}.\footnote{According to CPS guidelines, household respondents must be at least 15 years old with sufficient household knowledge. When the proxy is `self,' the respondent ranges from 15 to 17 years old.} Since my analysis compares high and low bias states, estimates remain valid provided reporting patterns don't systematically differ between these contexts.

@@

My analysis employs a US population subsample; Table (\ref{tab:hispbygen}) demonstrates sufficient observations across generations. Consistent with literature on racial identity fluidity among Asian Americans, I document significant attrition among third-generation Asian Americans.\footnote{\textcite{duncanIdentifyingLaterGenerationDescendants2018,duncanSocioeconomicIntegrationImmigrant2018, antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020} document substantial identity attrition among various groups.} Table (\ref{tab:hispbygen}) displays these patterns: most first- and second-generation Asian Americans racially self-identify as Asian. Among first-generation Asian Americans, 96\% self-report Asian racial identity. Among second-generation Asian Americans, 73\% self-identify as Asian, while 31\% of third-generation Asian Americans choose Asian racial identification. Attrition among second- and third-generation Asian Americans primarily occurs among children from interracial families.

@@

I report main results from estimating equation (\ref{eq:identity_reg_bias}) in Figure (\ref{plot01-regression-gen}). I present results estimating the main specification for all generations in panel (A) and for first-, second-, and third-generation subsamples in panels (B), (C), and (D), respectively. Anti-Asian bias and Asian racial identity reporting exhibit negative associations. One standard deviation anti-Asian bias increases correlate with 9 percentage point decreases in Asian racial identity reporting. Among first- and second-generation Asian Americans, one standard deviation anti-Asian bias increases associate with 5 and 8 percentage point decreases in Asian racial identity reporting. The first-generation coefficient lacks statistical significance, but confidence intervals remain predominantly negative. Among third-generation Asian Americans, one standard deviation anti-Asian bias increases associate with 8 percentage point decreases in Asian racial identity reporting. Moreover, I find that---among all objectively Asian individuals---having a college-educated father or mother increases Asian racial identity reporting by 1 percentage point.

@@

@@

These findings indicate negative correlations between anti-Asian bias and Asian racial identity reporting among Asian Americans. While I don't aim establishing causal anti-Asian bias effects on Asian racial identity reporting, I illustrate correlations between bias and racial identification. These correlations suggest that depending on state bias levels, racial gaps relying on self-reported identity might overestimate or underestimate discrimination effects.

@@

Moreover, \textcite{duncanIntermarriageIntergenerationalTransmission2011} show reported Hispanic identification doesn't vary with household respondent identity. Additionally, I present main Asian racial identity reporting effects by household respondent in Table (\ref{tab:hispbyproxy}). Main reported Asian racial identity effects equal 72 percentage points when mothers serve as proxies, 72 percentage points when fathers serve as proxies, and 87 percentage points when children or other caregivers serve as household respondents.\footnote{According to Current Population Survey (CPS) guidelines, household respondents must be at least 15 years old with sufficient household knowledge. When the proxy is `self,' respondents range from 15 to 17 years old.}

>>>>

I measure Asian racial identity using Current Population Survey (CPS) data from 2004-2021, enabling construction of objective Asian ancestry measures for minors living with parents. Following \textcite{antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020}, I utilize birthplace information for individuals, parents, and grandparents to create objective Asian ancestry indicators.\footnote{This approach parallels previous research but focuses on racial rather than ethnic categorization.} The methodology allows perfect identification of first-, second-, and third-generation Asian Americans (see Figure \ref{fig:diag} for visual representation). This approach enables construction of objective Asian ancestry measures for minors under age 17 living with parents. I also use another CPS sample of adults aged 18+ to examine whether their racial identity reporting patterns differ from minors. For the adult sample, I can only identify first- and second-generation.\footnote{Since adults still living with parents are might not representative of the overall adult population and is a rare occurrence, I do not link adults to their parents.}

The objective ancestry measure—distinct from subjective racial identification where respondents select ``Asian'' as their race—depends on birthplaces across three generations. The three identifiable generations include: 1) first-generation immigrants born in Asian countries with both parents also born in Asian countries, 2) second-generation individuals who are US-born citizens with at least one parent born in an Asian country, 3) third-generation Asian Americans who are US-born citizens with two US-born parents and at least one grandparent born in an Asian country. It is important to note that while the ancestry measure provides an objective assessment of Asian heritage, it may not capture all nuances of racial identity. For instance, White individuals with Asian ancestry born to non-Asian parents in Asia, such as on American military bases, may not be classified as Asian in the data. To avoid potential misclassification, I remove individuals who report that they were born abroad of American parents. The sample includes Asian Americans, first-, second-, and third-generation immigrants aged 17 and younger living with parents between 2004 and 2021. Summary statistics appear in Table (\ref{tab:sumstat1}). The adult sample includes first- and second-generation Asian American immigrants aged 18 and older between 2004 and 2021. The summary statistics for the adult sample appear in Table (\ref{tab:sumstat-adults}).

While CPS relies on household respondents (parents or caregivers) to report children's racial identity, this proxy reporting likely reflects children's actual identity since parents significantly influence identity formation. \textcite{duncanIntermarriageIntergenerationalTransmission2011} support this perspective, demonstrating no variation in Asian identification based on household respondent type. The data confirms consistent Asian identity reporting regardless of whether mother (72\%), father (72\%), or child/other caregiver (87\%) serves as respondent, as shown in Table \ref{tab:hispbyproxy}.\footnote{According to CPS guidelines, household respondents must be at least 15 years old with sufficient household knowledge. When the proxy is `self,' the respondent ranges from 15 to 17 years old.} Since my analysis compares high and low bias states, estimates remain valid provided reporting patterns don't systematically differ between these contexts. Furthermore, ethnic attrition patterns among adults align with those observed in children, as shown in Table (\ref{tab:hispbygen-adults}), suggesting that proxy reporting aligns with individuals' self-identification.

@@

My analysis employs a US population subsample; Table (\ref{tab:hispbygen}) demonstrates sufficient observations across generations. Consistent with literature on racial identity fluidity among Asian Americans, I document significant attrition among third-generation Asian Americans.\footnote{\textcite{duncanIdentifyingLaterGenerationDescendants2018,duncanSocioeconomicIntegrationImmigrant2018, antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020} document substantial identity attrition among various groups.} Table (\ref{tab:hispbygen}) displays these patterns: most first- and second-generation Asian Americans racially self-identify as Asian. Among first-generation Asian Americans, 96\% self-report Asian racial identity. Among second-generation Asian Americans, 73\% self-identify as Asian, while 31\% of third-generation Asian Americans choose Asian racial identification. Attrition among second- and third-generation Asian Americans primarily occurs among children from interracial families. The pattern among adults---see Table (\ref{tab:hispbygen-adults})---is similar, with 96\% of first-generation and 73\% of second-generation Asian Americans self-identifying as Asian. Breaking down by interracial families, second-generation Asian Americans with Asian parents report 95\% Asian identification, while those with one Asian and one White parent report 37\% Asian identification.

@@

I report main results from estimating equation (\ref{eq:identity_reg_bias}) in Figure (\ref{plot01-regression-gen}). I present results estimating the main specification for all generations in panel (A) and for first-, second-, and third-generation subsamples in panels (B), (C), and (D), respectively. Anti-Asian bias and Asian racial identity reporting exhibit negative associations. One standard deviation anti-Asian bias increases correlate with 9 percentage point decreases in Asian racial identity reporting. Among first- and second-generation Asian Americans, one standard deviation anti-Asian bias increases associate with 5 and 8 percentage point decreases in Asian racial identity reporting. The first-generation coefficient lacks statistical significance, but confidence intervals remain predominantly negative. Among third-generation Asian Americans, one standard deviation anti-Asian bias increases associate with 8 percentage point decreases in Asian racial identity reporting. Moreover, I find that---among all objectively Asian individuals---having a college-educated father or mother increases Asian racial identity reporting by 1 percentage point.\footnote{I show the results using county-level and MSA-level anti-Asian bias measures from the Implicit Association Test (IAT) show similar patterns. I present the county-level results in Figures \ref{plot01-regression-gen-county} and \ref{plot01-regression-byparent-county}, while I show the MSA-level in Figures \ref{plot01-regression-gen-msa} and \ref{plot01-regression-byparent-msa}.}

I report the results using adult samples in Figure (\ref{plot01-regression-gen-adults}). I present results estimating the main specification for all adults in panel (A) and for first- and second-generation subsamples in panels (B) and (C), respectively. Anti-Asian bias and Asian racial identity reporting exhibit negative associations. One standard deviation anti-Asian bias increases correlate with 5 percentage point decreases in Asian racial identity reporting. Among first-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 2 percentage point decreases in Asian racial identity reporting but is statistically insignificant. Among second-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting.

@@

I report the results using adult samples in Figure (\ref{plot01-regression-byparent-adults}). I present results estimating the main specification for all second-generation adults in panel (A) and for AA, AW, and WA children subsamples in panels (B), (C), and (D), respectively. One standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting among second-generation adults. Among second-generation adults with endogamous parents, one standard deviation anti-Asian bias increases associate with 10 percentage point decreases in Asian racial identity reporting but are statistically insignificant. However, one standard deviation anti-Asian bias increases associate with a statistically insignificant 3 percentage point decreases in Asian racial identity reporting among Asian father-White mother adults, and 24 percentage point decreases among White father-Asian mother adults.

@@

These findings indicate negative correlations between anti-Asian bias and Asian racial identity reporting among Asian Americans. Consequently, suggesting that depending on state bias levels, racial gaps relying on self-reported identity might overestimate or underestimate discrimination effects.

@@

Moreover, \textcite{duncanIntermarriageIntergenerationalTransmission2011} show reported Hispanic identification doesn't vary with household respondent identity. Additionally, I present main Asian racial identity reporting effects by household respondent in Table (\ref{tab:hispbyproxy}). Main reported Asian racial identity effects equal 72 percentage points when mothers serve as proxies, 72 percentage points when fathers serve as proxies, and 87 percentage points when children or other caregivers serve as household respondents.\footnote{According to Current Population Survey (CPS) guidelines, household respondents must be at least 15 years old with sufficient household knowledge. When the proxy is `self,' respondents range from 15 to 17 years old.}. To further address this concern, I examine adult Asian American samples where individuals self-report racial identity. I find similar patterns of ethnic attrition and bias effects among adults, as shown in Table (\ref{tab:hispbygen-adults}) and Figures (\ref{plot01-regression-gen-adults}-\ref{plot01-regression-byparent-adults}).

### 2025-09-07 submissions/03-jpam-RR/manuscript_online_appendix.tex
addressed R1's comments

\section{Tables} % (fold)
\label{sec:tabs-ap}

\input{tab33-asianiat_regression_tab.tex}

@@

>>>>

\section{Tables} % (fold)
\label{sec:tabs-ap}
\input{tab33-asianiat_regression_tab.tex}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Relationship Between Self-Reported Asian Identity and Bias: By Generation at the County Level}
\label{plot01-regression-gen-county}
%First graph
\begin{subfigure}{.48\textwidth}
\caption{All Generations}
\centering
\includegraphics[width=.9\linewidth]{county-by-parents-regs-all.png}
\end{subfigure}
\centering
%Second graph
\begin{subfigure}{.48\textwidth}
\caption{First-Generation}
\centering
\includegraphics[width=.9\linewidth]{county-skin-iat-regression-first-gen.png}
\end{subfigure}
%Third Graph
\begin{subfigure}{.48\textwidth}
\caption{Second-Generation}
\centering
\includegraphics[width=.9\linewidth]{county-skin-iat-regression-second-gen.png}
\end{subfigure}
%Fourth Graph
\begin{subfigure}{.48\textwidth}
\caption{Third-Generation}
\centering
\includegraphics[width=.9\linewidth]{county-skin-iat-regression-third-gen.png}
\end{subfigure}
\caption*{\footnotesize{I show four panels of estimating the effect of county-level anti-Asian implicit bias. I include state and year fixed effects with controls for sex, quartic age, and parental education. The dependent variable is self-reported Asian identity and the independent variable is county-level bias. Each panel is the results from the same regression but on different samples that are divided by generation. Standard errors are clustered on the state level. The samples include first-, second-, and third-generation Asian children ages 17 and below who live in intact families. First-generation Asian immigrants are children that were born in a Asian country. Native-born second-generation Asian immigrants are children with at least one parent born in a Asian country. Finally, native-born third-generation Asian immigrants are children with native-born parents and at least one grandparent born in a Asian country.}}
\end{figure}
\end{center}

\pagebreak
\newpage

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Relationship Between Self-Reported Asian Identity and Bias: By Parental Types at the County Level}
\label{plot01-regression-byparent-county}
%First graph
\begin{subfigure}{.48\textwidth}
\caption{Second-Generation (All Parental Types)}
\centering
\includegraphics[width=.9\linewidth]{county-by-parents-regs-all.png}
\end{subfigure}
\centering
%Second graph
\begin{subfigure}{.48\textwidth}
\caption{Asian Fathers-Asian Mothers}
\centering
\includegraphics[width=.9\linewidth]{county-by-parents-regs-hh.png}
\end{subfigure}
%Third Graph
\begin{subfigure}{.48\textwidth}
\caption{Asian Fathers-White Mothers}
\centering
\includegraphics[width=.9\linewidth]{county-by-parents-regs-hw.png}
\end{subfigure}
%Fourth Graph
\begin{subfigure}{.48\textwidth}
\caption{White Fathers-Asian Mothers}
\centering
\includegraphics[width=.9\linewidth]{county-by-parents-regs-wh.png}
\end{subfigure}
\caption*{\footnotesize{I show four panels of estimating the effect of county-level anti-Asian implicit bias---using the implicit association test (IAT) scores. I include state and year fixed effects with controls for sex, quartic age, and parental education. The dependent variable is self-reported Asian identity and the independent variable is county-level bias. Each panel results from the same regression but on different samples divided by parental types. Standard errors are clustered on the state level. The samples include second-generation Asian children ages 17 and below who live in intact families. Native-born second-generation Asian immigrant children with at least one parent born in an Asian country.}}
\end{figure}
\end{center}

\pagebreak
\newpage

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Relationship Between Self-Reported Asian Identity and Bias: By Generation at the MSA Level}
\label{plot01-regression-gen-msa}
%First graph
\begin{subfigure}{.48\textwidth}
\caption{All Generations}
\centering
\includegraphics[width=.9\linewidth]{msa-by-parents-regs-all.png}
\end{subfigure}
\centering
%Second graph
\begin{subfigure}{.48\textwidth}
\caption{First-Generation}
\centering
\includegraphics[width=.9\linewidth]{msa-skin-iat-regression-first-gen.png}
\end{subfigure}
%Third Graph
\begin{subfigure}{.48\textwidth}
\caption{Second-Generation}
\centering
\includegraphics[width=.9\linewidth]{msa-skin-iat-regression-second-gen.png}
\end{subfigure}
%Fourth Graph
\begin{subfigure}{.48\textwidth}
\caption{Third-Generation}
\centering
\includegraphics[width=.9\linewidth]{msa-skin-iat-regression-third-gen.png}
\end{subfigure}
\caption*{\footnotesize{I show four panels of estimating the effect of MSA-level anti-Asian implicit bias. I include state and year fixed effects with controls for sex, quartic age, and parental education. The dependent variable is self-reported Asian identity and the independent variable is MSA-level bias. Each panel is the results from the same regression but on different samples that are divided by generation. Standard errors are clustered on the state level. The samples include first-, second-, and third-generation Asian children ages 17 and below who live in intact families. First-generation Asian immigrants are children that were born in a Asian country. Native-born second-generation Asian immigrants are children with at least one parent born in a Asian country. Finally, native-born third-generation Asian immigrants are children with native-born parents and at least one grandparent born in a Asian country.}}
\end{figure}
\end{center}

\pagebreak
\newpage

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Relationship Between Self-Reported Asian Identity and Bias: By Parental Types at the MSA Level}
\label{plot01-regression-byparent-msa}
%First graph
\begin{subfigure}{.48\textwidth}
\caption{Second-Generation (All Parental Types)}
\centering
\includegraphics[width=.9\linewidth]{county-by-parents-regs-all.png}
\end{subfigure}
\centering
%Second graph
\begin{subfigure}{.48\textwidth}
\caption{Asian Fathers-Asian Mothers}
\centering
\includegraphics[width=.9\linewidth]{county-by-parents-regs-hh.png}
\end{subfigure}
%Third Graph
\begin{subfigure}{.48\textwidth}
\caption{Asian Fathers-White Mothers}
\centering
\includegraphics[width=.9\linewidth]{county-by-parents-regs-hw.png}
\end{subfigure}
%Fourth Graph
\begin{subfigure}{.48\textwidth}
\caption{White Fathers-Asian Mothers}
\centering
\includegraphics[width=.9\linewidth]{county-by-parents-regs-wh.png}
\end{subfigure}
\caption*{\footnotesize{I show four panels of estimating the effect of county-level anti-Asian implicit bias---using the implicit association test (IAT) scores. I include state and year fixed effects with controls for sex, quartic age, and parental education. The dependent variable is self-reported Asian identity and the independent variable is county-level bias. Each panel results from the same regression but on different samples divided by parental types. Standard errors are clustered on the state level. The samples include second-generation Asian children ages 17 and below who live in intact families. Native-born second-generation Asian immigrant children with at least one parent born in an Asian country.}}
\end{figure}
\end{center}

\pagebreak
\newpage

### 2025-09-07 submissions/03-jpam-RR/manuscript_tab_fig.tex
addressed R1's comments

@@

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Relationship Between Self-Reported Asian Identity and Bias: By Parental Types}
\label{plot01-regression-byparent}
%First graph
\begin{subfigure}{.48\textwidth}
\caption{Second-Generation (All Parental Types)}
\centering
\includegraphics[width=.9\linewidth]{by-parents-regs-all.png}
\end{subfigure}
\centering
%Second graph
\begin{subfigure}{.48\textwidth}
\caption{Asian Fathers-Asian Mothers}
\centering
\includegraphics[width=.9\linewidth]{by-parents-regs-hh.png}
\end{subfigure}
%Third Graph
\begin{subfigure}{.48\textwidth}
\caption{Asian Fathers-White Mothers}
\centering
\includegraphics[width=.9\linewidth]{by-parents-regs-hw.png}
\end{subfigure}
%Fourth Graph
\begin{subfigure}{.48\textwidth}
\caption{White Fathers-Asian Mothers}
\centering
\includegraphics[width=.9\linewidth]{by-parents-regs-wh.png}
\end{subfigure}
\caption*{\footnotesize{I show four panels of estimating equation (\ref{eq:identity_reg_bias}). I include region $\times$ year fixed effects with controls for sex, quartic age, and parental education. The dependent variable is self-reported Asian identity and the independent variable is state-level bias. Each panel results from the same regression but on different samples divided by parental types. Standard errors are clustered on the state level. The samples include second-generation Asian children ages 17 and below who live in intact families. Native-born second-generation Asian immigrant children with at least one parent born in a Spanish-speaking country.}}
\end{figure}
\end{center}

@@

>>>>

\input{tab53-SumStatOverAll-adults}

@@

\input{tab54-observations-by-gen-adults}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Relationship Between Self-Reported Asian Identity and Bias: By Generation Among Adults}
\label{plot01-regression-gen-adults}
%First graph
\begin{subfigure}{.48\textwidth}
\caption{All Generations}
\centering
\includegraphics[width=.9\linewidth]{skin-iat-regression-all-gens-adults.png}
\end{subfigure}
\centering
%Second graph
\begin{subfigure}{.48\textwidth}
\caption{First-Generation}
\centering
\includegraphics[width=.9\linewidth]{skin-iat-regression-first-gen-adults.png}
\end{subfigure}
%Third Graph
\begin{subfigure}{.48\textwidth}
\caption{Second-Generation}
\centering
\includegraphics[width=.9\linewidth]{skin-iat-regression-second-gen-adults.png}
\end{subfigure}

\caption*{\footnotesize{I show three panels of estimating equation (\ref{eq:identity_reg_bias}) on a sample of adults. I include region $\times$ year fixed effects with controls for sex, quartic age, years of education, and inverse hyperbolic sine of income. The dependent variable is self-reported Asian identity and the independent variable is state-level bias. Each panel is the results from the same regression but on different samples that are divided by generation. Standard errors are clustered on the state level. The samples include first- and second-generation Asian adults ages 18 and above. First-generation Asian immigrants are individuals that were born in a Asian country. Native-born second-generation Asian immigrants are individuals with at least one parent born in a Asian country.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Relationship Between Self-Reported Asian Identity and Bias: By Parental Types}
\label{plot01-regression-byparent}
%First graph
\begin{subfigure}{.48\textwidth}
\caption{Second-Generation (All Parental Types)}
\centering
\includegraphics[width=.9\linewidth]{by-parents-regs-all.png}
\end{subfigure}
\centering
%Second graph
\begin{subfigure}{.48\textwidth}
\caption{Asian Fathers-Asian Mothers}
\centering
\includegraphics[width=.9\linewidth]{by-parents-regs-hh.png}
\end{subfigure}
%Third Graph
\begin{subfigure}{.48\textwidth}
\caption{Asian Fathers-White Mothers}
\centering
\includegraphics[width=.9\linewidth]{by-parents-regs-hw.png}
\end{subfigure}
%Fourth Graph
\begin{subfigure}{.48\textwidth}
\caption{White Fathers-Asian Mothers}
\centering
\includegraphics[width=.9\linewidth]{by-parents-regs-wh.png}
\end{subfigure}
\caption*{\footnotesize{I show four panels of estimating equation (\ref{eq:identity_reg_bias}). I include region $\times$ year fixed effects with controls for sex, quartic age, and parental education. The dependent variable is self-reported Asian identity and the independent variable is state-level bias. Each panel results from the same regression but on different samples divided by parental types. Standard errors are clustered on the state level. The samples include second-generation Asian children ages 17 and below who live in intact families. Native-born second-generation Asian immigrant children with at least one parent born in an Asian country.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Relationship Between Self-Reported Asian Identity and Bias: By Parental Types Among Adults}
\label{plot01-regression-byparent-adults}
%First graph
\begin{subfigure}{.48\textwidth}
\caption{Second-Generation (All Parental Types)}
\centering
\includegraphics[width=.9\linewidth]{by-parents-regs-all-adults.png}
\end{subfigure}
\centering
%Second graph
\begin{subfigure}{.48\textwidth}
\caption{Asian Fathers-Asian Mothers}
\centering
\includegraphics[width=.9\linewidth]{by-parents-regs-hh-adults.png}
\end{subfigure}
%Third Graph
\begin{subfigure}{.48\textwidth}
\caption{Asian Fathers-White Mothers}
\centering
\includegraphics[width=.9\linewidth]{by-parents-regs-hw-adults.png}
\end{subfigure}
%Fourth Graph
\begin{subfigure}{.48\textwidth}
\caption{White Fathers-Asian Mothers}
\centering
\includegraphics[width=.9\linewidth]{by-parents-regs-wh-adults.png}
\end{subfigure}
\caption*{\footnotesize{I show four panels of estimating equation (\ref{eq:identity_reg_bias}) on a sample of adults. I include region $\times$ year fixed effects with controls for sex, quartic age, years of education, and the inverse hyperbolic sine of income. The dependent variable is self-reported Asian identity and the independent variable is state-level bias. Each panel results from the same regression but on different samples divided by parental types. Standard errors are clustered on the state level. The samples include second-generation Asian individuals ages 18 and above. Native-born second-generation Asian immigrant individuals with at least one parent born in an Asian country.}}
\end{figure}
\end{center}

@@

% \input{tab06-regression_tab_byproxy_skin.tex}
% \pagebreak
% \newpage
